P.berghei pir calculate TPM

### 2021-09-06 chapter3_results_bergheiPir/Manuscript_Github_Pberghei_CalculateTPM.Rmd
Save hclust plots from berg

```{r load_packages, include = FALSE, message = FALSE}
library('readxl')
library('readr')
library('dplyr')
library('purrr')
library('ggplot2')
library('DESeq2')
library("RColorBrewer")
library('colorspace')
library('data.table')
library('gridExtra')
library('tibble')
library('scales')
library('stringr')
library('kableExtra')
library('viridis')
library('corrplot')
library('reshape2')
library('circlize') # for circular plots
library('cluster')    # clustering algorithms
library('factoextra') # clustering algorithms & visualization
library('ggfortify') # so ggplot understands prcomp objects
library('ape') # for phylogeny plotting
library('dendextend') # for dendrogram plotting
library('plotly')
library('ggpattern')
library('ComplexHeatmap')

@@

all.equal(berghei_tpm[3345:3350,23:28],check_tpm)

@@

@@

lapply(experiment_id, 
       function(experiment_name){
         tpm_data <- select(berghei_tpm, matches(experiment_name))
         if(ncol(tpm_data) > 3){
           dists = dist(t(tpm_data))
           par(cex=0.7)
           plot(hclust(dists),
                main = experiment_name)
         }
       })

>>>>

```{r load_packages, include = FALSE, message = FALSE}
library('readxl')
library('readr')
library('dplyr')
library('purrr')
library('ggplot2')
library('DESeq2')
library("RColorBrewer")
library('colorspace')
library('data.table')
library('gridExtra')
library('tibble')
library('scales')
library('stringr')
library('kableExtra')
library('viridis')
library('corrplot')
library('reshape2')
library('circlize') # for circular plots
library('cluster')    # clustering algorithms
library('factoextra') # clustering algorithms & visualization
library('ggfortify') # so ggplot understands prcomp objects
library('ape') # for phylogeny plotting
library('dendextend') # for dendrogram plotting
library('plotly')
library('ggpattern')
library('ComplexHeatmap')
library('ggdendro') #Drawing ggplot dendrograms

@@

all.equal(berghei_tpm[3345:3350,colnames(check_tpm)],check_tpm)

@@

# Hierarchical clustering plots.

@@

lapply(experiment_id, 
       function(experiment_name){
         tpm_data <- select(berghei_tpm, matches(experiment_name))
         if(ncol(tpm_data) > 3){
           dists = dist(t(tpm_data))
           par(cex=0.7)
           p <- ggdendrogram(hclust(dists)) +
             ggtitle(experiment_name)
           ggsave(filename = paste0('thesis_chapter3_figure_hclust_', 
                                    experiment_name, 
                                    '.png'),
                  plot = p,
                  path = 'plots')
           return(p)
         }
       }
)
```
